Conclusion
- What have you learnt from the research? What are surprising findings
  from the work? What future work is possible? Some additional
  insights. The conclusion is very different from the abstract!


--------------------------------------------------------------------------------
Imagine a drunken reviewer who reads the paper, will s/he understand?
Is the paper sufficiently clear that even a drunken reviewer gets it?
--------------------------------------------------------------------------------
- Replace an assumption by an observation. It's much easier to disagree
  with an assumption than with an observation!
- Always keep the reader informed on where in the paper s/he is, where
  the paper is heading toward, always make it clear what else is
  expected, what is still coming up
- Make sure that mechanism is concisely explained, so that results are
  repeatable.
- State the main result upfront, then back it up with the text. Poor
  writing is to explain things in a lot of text and the main point
  doesn't really jump out. For example, in poorly structured text the
  reader has to pay careful attention to assemble the train of thought
  as she's reading the section.
- Use phrases such as "we find that", "we discovered that"
- Use "because" often, people seem to believe whatever comes thereafter.
- Careful with the terms "correct", "optimal", or "proof"! People have
  varying opinions of correctness, so it's likely that someone
  misunderstands it. Especially theory people are very particular
  about this term.
